QPLIB: A Library of Quadratic Programming Instances

### 2018-02-05 QPLIB-2.1.tex
consistent title case in section headers
Update QPLIB-2.1.tex

\textcolor{red}{In the rest of this paper, we shall sometimes refer to {\it exact solutions} of quadratic programs. In view of the fact that their solutions may be irrational, this notation deserves a comment. If the decision version of the problem being referred to is in NP (e.g.~LP, MILP, QP \cite{vavasis90a}), then the assumption is that all rational numbers can be represented exactly by a Turing Machine (TM). 
%This assumption has the same limitation as the assumption that TMs defined on integers are a faithful abstraction of a real computer, namely that the range of integers needing a representation is bounded. 
If there is no known proof that the problem being solved (or its decision version) is in NP, then there are four main approaches:
\begin{enumerate}
\item finding a representable solution $x'$ such that $\|x'-x^\ast\|_\infty\le\varepsilon$, where $x^\ast$ is the true solution, $\varepsilon>0$ is given, and representable means having a polynomially sized description length
% ``
(in function of the instance size) \cite{hochbaum2};
\item using the {\it Thom encoding} of an algebraic number \cite[Prop.~2.28]{pollack} (limited to problems involving polynomials);
\item using the optimality gap: finding a representable solution $x'$ such that $|f(x')-f(x^\ast)|\le\varepsilon$, where $f$ is the objective function, $x^\ast$ is the true solution, $\varepsilon>0$ is given
%, and representable is as above 
(limited to optimization problems);\label{optgap}
\item using a computational model according to which every elementary computation on the reals takes $O(1)$ and returns a precise result \cite[p.~24]{blum}.
\end{enumerate}
Approach \ref{optgap} in the list above is the one most often used in computational papers, including the present one.}

>>>>

\textcolor{red}{In the rest of this paper, we shall sometimes refer to {\it exact solutions} of quadratic programs. In view of the fact that their solutions may be irrational, this notation deserves a comment. If the decision version of the problem being referred to is in NP (e.g.~LP, MILP, QP \cite{vavasis90a}), then the assumption is that all rational numbers can be represented exactly by a Turing Machine (TM). 
%This assumption has the same limitation as the assumption that TMs defined on integers are a faithful abstraction of a real computer, namely that the range of integers needing a representation is bounded. 
If there is no known proof that the problem being solved (or its decision version) is in NP, then there are four main approaches:
\begin{enumerate}
\item finding a representable solution $x'$ such that $\|x'-x^\ast\|_\infty\le\varepsilon$, where $x^\ast$ is the true solution, $\varepsilon>0$ is given, and representable means having a polynomially sized description length
% ``
(in function of the instance size) \cite{hochbaum2};
\item using the {\it Thom encoding} of an algebraic number \cite[Prop.~2.28]{pollack} (limited to problems involving polynomials);
\item using the optimality gap: finding a representable solution $x'$ such that $|f(x')-f(x^\ast)|\le\varepsilon$, where $f$ is the objective function, $x^\ast$ is the true solution, $\varepsilon>0$ is given
%, and representable is as above 
(limited to optimization problems);\label{optgap}
\item using a computational model according to which every elementary computation on the reals takes $O(1)$ and returns an exact result \cite[p.~24]{blum}.
\end{enumerate}
Approach \ref{optgap} in the list above is the one most often used in computational papers, including the present one.}
